A NetdiffuseR Tutorial: Estimating Network Influences on Behavior within the Diffusion Paradigm

### 2024-12-05 paper.qmd
Adding final example

```{r}
#| label: age-homophilic-exp
# Using homophilic distance
exp_age_homo <- vertex_covariate_compare(
 graph   = kfam_diffnet$graph[[1]],
 X       = cbind(kfam_diffnet[["age"]]),
 funname = "distance"
)

# Inverting the values
exp_age_homo@x <- 1/exp_age_homo@x

exp_age_homo <- exposure(
 kfam_diffnet, alt.graph = exp_age_homo,
 valued = TRUE
 )

@@

>>>>

```{r}
#| label: age-homophilic-exp
# Using homophilic distance
exp_age_homo_graph <- vertex_covariate_compare(
 graph   = kfam_diffnet$graph[[1]],
 X       = cbind(kfam_diffnet[["age"]]),
 funname = "distance"
)

# Inverting the values
exp_age_homo_graph@x <- 1/exp_age_homo_graph@x

exp_age_homo <- exposure(
 kfam_diffnet,
 alt.graph = exp_age_homo_graph,
 valued = TRUE
 )

@@

## Fitting a lagged exposure model

A natural step after computing exposures is estimating lagged exposure models. The most common approach is fitting a logistic regression that predicts the adoption of a behavior as a function of the nodes' features and lagged exposure. The netdiffuseR package has a number of tools to facilitate this process, but maybe the most useful is the `diffreg` function. The following code shows how to fit a diffusion model using the default exposure calculation:

```{r}
#| label: diffreg
diffreg(kfam_diffnet ~ exposure) |>
  summary()
```

We can go further and add more features from the Korean family dataset, including computing more complex exposures as we did before:

```{r}
#| label: diffreg-2
#| warning: false
diffreg(
  kfam_diffnet ~ age + factor(village) +
    exposure(
      alt.graph = exp_age_homo_graph,
      valued = TRUE
      )
  ) |>
  summary()
```

As you can see, we can pass arguments to the `exposure` function on the fly, including using the R's formula interface which is commonly used with the `glm` function in the package. More details about what happens when calling the `diffreg` function can be found in the function's manual.
